Spatiotemporal transmission risk

### 2023-03-29 analysis/spatiotemporal-transmission-risk.Rmd
minor changes to spatiotemporal model

# building
cellSize <- sqrt(1 * 1e9 / 3e3) 
building <- terra::vect(paste("../data-raw", "Masi", "building", "clinic-vector.gpkg", sep = "/"))
building_sf <- sf::st_as_sf(building, crs = NA)
sf::st_crs(building_sf) <- NA
waiting_room <- shapeToSpatial(building_sf$geometry[2], cellSize)
waiting_room_df <- fortify(waiting_room)
passage <- shapeToSpatial(building_sf$geometry[4], cellSize)
passage_df <- fortify(passage)
tb_room <- shapeToSpatial(building_sf$geometry[3], cellSize)
tb_room_df <- fortify(tb_room)

# test
# waiting_room_df$value <- rnorm(nrow(waiting_room_df))
# passage_df$value <- rnorm(nrow(passage_df))
# tb_room_df$value <- rnorm(nrow(tb_room_df))
# 
# ggplot(mapping = aes(x = long, y = lat, group = group, fill = value)) +
#   geom_polygon(data = waiting_room_df) +
#   geom_polygon(data = passage_df) +
#   geom_polygon(data = tb_room_df) +
#   ggpubr::background_image(clinic_img) +
#   annotate("text", x = -13200, y = -5300, label = "Entrance", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
#   annotate("text", x = -13400, y = -2300, label = "Waiting room", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
#   annotate("text", x = -5000, y = -4100, label = "Registration", size = 8 / cm(1), fontface = 2, angle = 90, hjust=0,vjust=0) +
#   annotate("text", x = 2600, y = -2700, label = "TB room", size = 8 / cm(1), fontface = 2) +
#   scale_y_continuous(expand = expansion(add=c(2500, 4000))) +
#   scale_x_continuous(expand = expansion(add=c(400, 500))) +
#   labs(fill = "Density") +
#   theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
#         legend.position = c(0.825,0.075), legend.direction = "horizontal", legend.title = element_blank(), #legend.title = element_text(vjust = .75),
#         panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 3, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank())
```

@@

qc_pl <- ggplot(mapping = aes(x = long, y = lat, group = group, fill = N)) +
  geom_polygon(data = quantaConc_av_wr) +
  geom_polygon(data = quantaConc_av_pa) +
  geom_polygon(data = quantaConc_av_tb) +
  ggpubr::background_image(clinic_img) +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log1p", labels = function(x) x * 1000, breaks = c(.1, .5, 1, .15, 2)/1000) +
  scale_y_continuous(expand = expansion(add=c(2500, 3250))) +
  scale_x_continuous(expand = expansion(add=c(400, 500))) +
  facet_wrap(~daytime, ncol = 1) +
  annotation_custom(entrance_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(wr_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(tb_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(re_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  labs(fill = expression("Density (10"^-3*"quanta/m"^3*")")) +
  theme_classic() +
  theme(text = element_text(size = text_descr),
        axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
        legend.position = c(0.825,0.05), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  guides(fill = guide_legend(title.position = "top"))
qc_pl
ggsave(plot = qc_pl, filename = "../doc/IWHOD/presentation/figures/quanta-concentration.png", width = width_descr * 1.5, height = height_descr * 2)
```

>>>>

# building
cellSize <- sqrt(1 * 1e9 / 3e3) 
building <- terra::vect(paste("../data-raw", "Masi", "building", "clinic-vector.gpkg", sep = "/"))
building_sf <- sf::st_as_sf(building, crs = NA)
sf::st_crs(building_sf) <- NA
waiting_room <- shapeToSpatial(building_sf$geometry[2], cellSize)
waiting_room_df <- fortify(waiting_room)
passage <- shapeToSpatial(building_sf$geometry[4], cellSize)
passage_df <- fortify(passage)
tb_room <- shapeToSpatial(building_sf$geometry[3], cellSize)
tb_room_df <- fortify(tb_room)
```

@@

qc_pl <- ggplot(mapping = aes(x = long, y = lat, group = group, fill = N)) +
  geom_polygon(data = quantaConc_av_wr) +
  geom_polygon(data = quantaConc_av_pa) +
  geom_polygon(data = quantaConc_av_tb) +
  ggpubr::background_image(clinic_img) +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log1p", labels = function(x) x * 1000, breaks = c(.1, .5, 1, .15, 2)/1000) +
  scale_y_continuous(expand = expansion(add=c(2500, 3250))) +
  scale_x_continuous(expand = expansion(add=c(400, 500))) +
  facet_wrap(~daytime, ncol = 1) +
  annotation_custom(entrance_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(wr_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(tb_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(re_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  labs(fill = expression("Density (10"^-3*"quanta/m"^3*")")) +
  theme_classic() +
  theme(text = element_text(size = text_descr),
        axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
        legend.position = c(0.825,0.05), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  guides(fill = guide_legend(title.position = "top"))
qc_pl
ggsave(plot = qc_pl, filename = "../doc/IWHOD/presentation/figures/quanta-concentration.png", width = width_descr * 1.5, height = height_descr * 2)

# for abstract
highRiskPat_pl_abs <- highRiskPat_pl +
  labs(title = "1a | Estimated no. of attendees with high-risk of MtB infection",
       subtitle = "Number (mean and 95%-limits) of high-risk clinical attendees (defined as P>1%)") +
  theme(plot.title = element_text(face = 2),
        plot.title.position = "plot")

summary_tab_abs <- summary_tab +
  labs(title = " ",
       subtitle = " ")

qc_pl_abs <- qc_pl +
  labs(title = "1b | Estimated quanta concentration in the clinic by daytime",
        subtitle = "Average concentration in the morning (7:30 to 12am) and afternoon (12am to 4pm)") +
  theme(plot.title = element_text(face = 2))

comb_abs_pl <- grid.arrange(grid.arrange(highRiskPat_pl_abs, summary_tab_abs, ncol = 2, widths = 16 * c(0.7,.3)), qc_pl_abs, ncol = 1, heights = 25 / cm(1) * c(0.35, 0.65))
ggsave(plot = comb_abs_pl, filename = "../doc/Union/abstract/figure.png", width = 16 / cm(1), height = 25 / cm(1))
```
